---
title: "KaggleSurvey2018"
output: html_document
---

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# install all missing packages
list.of.packages <- c('ggplot2', 'tidyverse', 'data.table', 'purrr', 'GGally')

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
```

```{r}
# set working directory
getwd()

# load libraries
library(tidyverse)
library(ggplot2)
library(GGally)
library(data.table)
library(purrr)
```


# Read data

```{r}
# see: https://www.kaggle.com/kaggle/kaggle-survey-2018#multipleChoiceResponses.csv
raw <- read_csv('multipleChoiceResponses.csv')

#glimpse(raw)
head(raw)
```

# 開始 EDA

## 列出一些有趣的問題

* Q2	What is your age (# years)?
* Q3  Country
* Q6	Select the title most similar to your current role (or most recent title if retired): - Selected Choice
* Q23	Approximately what percent of your time at work or school is spent actively coding?

* Q24	How long have you been writing code to analyze data?
* Q25	For how many years have you used machine learning methods (at work or in school)?
* Q26	Do you consider yourself to be a data scientist?
* Q33	Where do you find public datasets? (Select all that apply) - Selected Choice


## The first row contains the text for each response, so we need to save it separately and then remove it from the df.


```{r}
#questions <- as.character(as.vector(all[1,]))
questionsDf <- raw[1,] # as df
questions <- t(raw[1,]) # as vector
all <- raw[-1,]
head(all)

head(questions)
```

## Preprocessing: isStudent?

Note: The answer to Q6 reveals this.

```{r}
all <- all %>% 
  mutate(isStudent = Q6 == 'Student')
```

## Some Utilities
```{r}

getQuestionText <- function(colName) {
  unname(unlist(subset(questionsDf, select = c(colName))))
}

getQuestion <- function(colName) {
  if (!(colName %in% names(questionsDf))) {
    colName <- paste0(colName, '_Part_1')
  }
  q <- getQuestionText(colName)
  parts <- unlist(strsplit(q, ' \\(Select all that apply\\) - Selected Choice - '))
  parts[1]
}

# in case the given column is a multi-part multichoice column, select only the choice
getQuestionChoice <- function(colName) {
  q <- getQuestionText(colName)
  parts <- unlist(strsplit(q, ' \\(Select all that apply\\) - Selected Choice - '))
  parts[2]
}

# see: https://stackoverflow.com/a/42125262
selectMultiPartQuestion <- function(qu) {
  # vars <- paste0("^(", paste(vars, collapse="|"), ")")
  # select(df, matches(vars))
  tmp <- all %>% select(starts_with(qu))
  cnames <- names(tmp)
  tmp <- tmp[, cnames != paste0(qu, '_OTHER_TEXT')] # drop OTHER_TEXT
  actualNames <- as.vector(na.omit(as.vector(sapply(tmp, unique))))
  #print(actualNames)
  colnames(tmp) <- actualNames
  
  # convert factors to boolean
  #colnames(tmp) <- 
  sapply(tmp, function(x) !is.na(x))
}

q33 <- selectMultiPartQuestion('Q33')

getQuestion('Q33')
colSums(q33)

#ggpairs(q33)

#q33 %>% ggplot(aes())
```
## 開始做一些實驗～

```{r}

selectOneQuestion <- function(mydf, qu) {
  #qs = c(qu)
  # why use enquo? - see: https://dplyr.tidyverse.org/articles/programming.html
  quo_qu <- enquo(qu)
  mydf %>%
    select(!!quo_qu) %>%
    group_by(!!quo_qu) %>%
    summarize(n = n()) %>%
    arrange(desc(n))
}

q6 <- all %>%
  select(Q6) %>%
  group_by(Q6) %>%
  summarize(n = n()) %>%
  arrange(desc(n))

head(q6)

makeQ23 <- function(data) {
  data %>% 
    select(Q23) %>%
    group_by(Q23) %>%
    summarize(n = n()) %>%
    arrange(desc(n))
}

q23 <- makeQ23(all)
head(q23)


unique(all$Q6)

q23_stu <- makeQ23(all %>% filter(isStudent == T))
head(q23_stu)

q2 <- selectOneQuestion(all, Q2)
head(q2)


```

## TODO; Take all "Other_text" columns into a separate data frame (to simplify handling multiple choice questions?)

```{r}
# see: https://stackoverflow.com/questions/30189979/select-columns-of-data-table-based-on-regex
# cols <- grep("bar|baz", names(all), value = TRUE)
# noOthers <- mydt[, ..cols]
```

```{r}
# take the first nQ questions
nQ <-  1:4
cols <- unlist(nQ %>% map(function(i) str_interp('Q${i}')))
qs <- all[, cols]
qs
```
