---
title: "EDA of HW1 result"
author: "Micc"
date: "2019年4月1日"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this report, I made some visualization from the data, showing some fun facts.

## Get started

#### Loading library
```{r libs, message=FALSE}
library(tidyverse)
library(magrittr)
```

#### Imorting data and preprocessing
```{r import}
# import data
df <- read.csv("export_replaced.csv", fileEncoding = "UTF-8", stringsAsFactors = F) %>%
    select(c("Username", "TotalXp", "NumExercisesCompleted", "NumCoursesCompleted", "CompletedCourses")) %>%
    replace_na(list(CompletedCourses = ""))
```

```{r preprocess}
# preprocess
df %<>%
    replace_na(list(CompletedCourses = "")) %>%
    mutate(CompletedCourses=strsplit(CompletedCourses, split=", "))
```

#### Have a look on the dataset
```{r view}
head(df)
str(df)
```

## Analysis

#### Tidy up the columns
To make visualization better, we need to tidy up the data, first we find out who has finished HW1.
```{r}
df %<>%
    mutate(Passed = TotalXp >= 10000)

head(df)
```

And since the column "CoursesFinished" is too messy to visualize, we need to change it's format.
```{r}
# find unique names
courseNames = df$CompletedCourses %>%
    unlist %>%
    unique

# create new columns in value of boolean
for(name in courseNames){
    df[, name] = sapply(df$CompletedCourses, function(x) is.element(name, x))
}

df = select(df, -c("CompletedCourses"))

head(df)
```

## Visualizations

#### Courses finished count
```{r}
# Count CoursesFinished
df[,courseNames] %>%
    colSums %>%
    data.frame(key=names(.), value=.) %>%
    ggplot(aes(key, value)) +
    geom_bar(stat="identity") +
    geom_text(aes(label=courseNames), position=position_dodge(width=0.9), hjust=-0.1, angle = 90) +
    theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank())

# beautify
df[,courseNames] %>%
    colSums %>%
    sort(decreasing=T) %>%
    data.frame(key=names(.), value=.) %>%
    filter(value > 5) %>%
    ggplot(aes(reorder(key, -value), value, fill=reorder(key, -value))) +
    geom_bar(stat="identity") +
    theme(axis.title.x=element_blank()) +
    ylab("人數") +
    guides(fill=guide_legend(title="課程名稱"))
```

#### Who finished it twice?
```{r}
# finished "Introduction to R" in two language
both = df %>%
    filter(`Introduction to R` == T, `R 語言導論`==T) %>%
    nrow

# finished "Introduction to R" in CH
inCH = sum(df[,"R 語言導論"])

# finished "Introduction to R" in EN
inEN = sum(df[,"Introduction to R"])

# visualize
data.frame(count= c(both, inCH, inEN), item=factor(c("both", "CH", "EN"))) %>%
    ggplot(aes(x=item, y=count, fill=item)) +
    geom_bar(stat="identity")
```

#### Histogram of TotalXp
```{r}
# TotalXP
df %>%
    mutate(TotalXp = TotalXp+1) %>% # 剛好10000分的人會被算在線的左邊
    ggplot(aes(TotalXp, fill=Passed)) +
    geom_histogram(binwidth=4000) +
    geom_vline(aes(xintercept=10000),
               color="black", linetype="dashed", size=0.5)

# boxplot
ggplot(df, aes(y=TotalXp)) + 
    geom_boxplot()
```

#### Scatter plot: "TotalXp" over "NumCoursesCompleted
```{r}
df %>%
    ggplot(aes(x=NumCoursesCompleted, y=TotalXp)) +
    geom_point(aes(col=Passed), position=position_jitter(width=.05)) +
    geom_smooth(method='lm',formula=y~x, se=F)
```